### 2013-11-11 src2/thesis.tex
update

Inputs to an Obsidian program are pull arrays. Pull arrays can be arbitrarily permuted; 
the permutation used will decide the access pattern. If global memory accesses can 
be coalesced or not partly also depends on the algorithm being implemented.

\item {\bf Minimise use of global memory:} Accessing global device memory can take as 
many as 400 to 600 clock cycles if the data is not cached. The programmer should 
use shared memory as much as possible to avoid redundant loading from global memory.
Shared memory can also be used to coalesce reads from global memory. Shared memory is 
a limited resource in the MP, so if a kernel uses very much shared memory, 
fewer such blocks can be active on the MP.

@@

Sometimes divergent code cannot be avoided. However, it is important not to have threads 
diverge unnecessarily. When using pull arrays alone, this was often a problem; with the 
addition of push arrays, the situation improved. Using push arrays, some divergent computations 
can be explicitly split up into phases, each phase with all threads following the 
same execution path. This means that fewer threads are required to do the same work.

>>>>

Inputs to an Obsidian program are pull arrays. Pull arrays can be arbitrarily permuted; 
the permutation used will decide the access pattern. In section~\ref{sec:OBSARRAYS}, there 
is more information about pull arrays. If global memory accesses can 
be coalesced or not partly also depends on the algorithm being implemented. The next paragraph 
suggests a trick for coalescing memory accesses, in some cases, even if the algorithm is 
unsuitable. Then it becomes a trade between bad memory access pattern and using more 
shared memory.

\item {\bf Minimise use of global memory:} Accessing global device memory can take as 
many as 400 to 600 clock cycles if the data is not cached, this is 10 - 20 times as many cycles 
as an access to shared memory. The programmer should use shared memory as much as possible 
to avoid redundant loading from global memory. Shared memory can also be used to coalesce 
reads from global memory. Shared memory is a limited resource in the MP, so if a kernel 
uses very much shared memory, fewer such blocks can be active on the MP.

@@

Sometimes divergent code cannot be avoided. However, it is important not to have threads 
diverge unnecessarily. When using pull arrays alone, this was often a problem; with the 
addition of push arrays, the situation improved. Using push arrays, some divergent computations 
can be explicitly split up into phases, each phase with all threads following the 
same execution path. This means that fewer threads are required to do the same work. Push arrays 
are explained in more detail in section~\ref{sec:OBSARRAYS}.
